Negative Perceptions of Outsourcing to Artificial Intelligence

### 2025-04-30 appendix.qmd
Editing manuscript and preparing for submission

::: {#suppfig-treatments-tasks-study3 suppfig-pos="H"}

```{r, fig.height=5, fig.width=8.5}
tar_read(plot_treatments_tasks_study4)
```

Variation in the effects of outsourcing across tasks in Study 3. Tasks are 
ordered from most social (top) to least social (bottom) according to ratings 
from a pilot study. Point ranges are differences in marginal means on a 7-point
Likert scale for the low effort conditions (red) and high effort conditions 
(blue) compared to the control condition. Upper panels refer to the standard LLM
conditions, and lower panels refer to the personalised LLM conditions. Points 
and ranges represent posterior medians and 95% credible intervals, respectively.

@@

::: {#suppfig-treatments-tasks-study4 suppfig-pos="H"}

```{r, fig.height=4, fig.width=8.5}
tar_read(plot_treatments_tasks_study5)
```

Variation in the effects of outsourcing across tasks in Study 4. Tasks are 
ordered from most social (top) to least social (bottom) according to ratings 
from a pilot study. Point ranges are differences in marginal means on a 7-point
Likert scale for the bad reason conditions (red) and good reason conditions 
(blue) compared to the control condition. Upper panels refer to the tool 
outsourcing conditions, and lower panels refer to the full outsourcing 
conditions. Points and ranges represent posterior medians and 95% credible 
intervals, respectively.

@@

@@

Pairwise comparisons of word frequencies between conditions. LL = log 
likelihood; %DIFF =

>>>>

@@

@@

::: {#suppfig-reasons-tasks-study4 suppfig-pos="H"}

```{r, fig.height=3.5, fig.width=8.5}
tar_read(plot_reasons_tasks_study5)
```

Variation in the effect of reasons across tasks in Study 4. Tasks are ordered 
from most social (top) to least social (bottom) according to ratings from a 
pilot study. Point ranges are differences in marginal means on a 7-point Likert 
scale between the "bad reason" and "good reason" conditions, split by 
outsourcing type. Points and ranges represent posterior medians and 95% credible 
intervals, respectively.

@@

Pairwise comparisons of word frequencies between conditions. LL = log 
likelihood.
